---
title: "Food label readability - Cross-sectional analysis 12112024"
author: "Constanza Avalos"
date: "2024-11-12"
output: 
  pdf_document:
    latex_engine: xelatex
    toc: yes
  word_document:
    toc: yes
  html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Clear cache

```{r cache}

# Clear the R package cache by removing the temporary directory
unlink(tempdir(), recursive = TRUE)

# Optionally, clear the .Rhistory file if needed
if (file.exists(".Rhistory")) {
  file.remove(".Rhistory")
}

# Clear the workspace
rm(list = ls())

```

## Introduction

+This study examines cross-sectional relationships between perceived multiple traffic light (MTL) legibility and self-reported processed food consumption frequency in the UK. 

## Importing data sets

Food and You Survey 2010-2018

```{r data}
#Load all necessary libraries
library(tidyverse) # Modern data science library
library(plm) # Panel data analysis library
library(car) # Companion to applied regression
library(gplots) # Various programing tools for plotting data
library(tseries) # For timeseries analysis
library(lmtest) # For hetoroskedasticity analysis
library(readr)
library(texreg)
library(ordinal)
library(VGAM)
library(survey)
#tinytex::install_tinytex()

df_full5waves <- read_csv("C:/Users/const/OneDrive/Desktop/PhD/Papers and Reports/Paper 2nd/4. Dataset/foodandyou-w1_5combined_FSA_Correctedseeking.csv")

ndns_data5_6 <- read_tsv("C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper 2/Data set NDNS/ndns_rp_yr5-6a_foodleveldietarydata_v2.tab")

ndns_data7_8 <- read_tsv("C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper 2/Data set NDNS/ndns_rp_yr7-8a_foodleveldietarydata.tab")

ndns_data9 <- read_tsv("C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper 2/Data set NDNS/ndns_rp_yr9a_foodleveldietarydata_uk_20210831.tab")

ndns_data10 <- read_tsv("C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper 2/Data set NDNS/ndns_rp_yr10a_foodleveldietarydata_uk_20210831.tab")

ndns_data11 <- read_tsv("C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper 2/Data set NDNS/ndns_rp_yr11a_foodleveldietarydata_uk_20210831.tab")

ndns_dataind5_6 <- read_tsv("C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper 2/Data set NDNS/ndns_rp_yr5-6a_indiv.tab")

ndns_dataind7_8 <- read_tsv("C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper 2/Data set NDNS/ndns_rp_yr7-8a_indiv.tab")

ndns_dataind9_11 <- read_tsv("C:/Users/cavalos/OneDrive - The Alan Turing Institute/Desktop/PhD CAV/Paper 2/Data set NDNS/ndns_rp_yr9_11a_indiv_20211020.tab")

```


## Checking data set FSA including survey weights


Age_Banded: 8 bands

5	16-17
6	18-19
7	20-24
8	25-34
9	35-44
10	45-54
11	55-64
12	65+
  
Age_dv: 7 bands

1	16-24
2	25-34
3	35-44
4	45-54
5	55-64
6	65-74
7	75+

5, 6 and 7 = 1 in Age_dv
8 = 2
9 = 3
10 = 4
11 = 5
12 = 11 and 12 Age_dv


```{r table4, echo=FALSE}

#COMPARABLE VARIABLES

#table(df_full5waves$RespSex, df_full5waves$surveyyear) #Comparable
#table(df_full5waves$age_dv, df_full5waves$surveyyear) # comparable
#table(df_full5waves$Age_Banded, df_full5waves$surveyyear) # comparable
#table(df_full5waves$below16, df_full5waves$surveyyear) # comparable
#table(df_full5waves$bhhsize, df_full5waves$surveyyear) # comparable
#table(df_full5waves$hhdinc, df_full5waves$surveyyear) # partially comparable recode
#table(df_full5waves$marstat2, df_full5waves$surveyyear) # comparable
#table(df_full5waves$Religion_DV, df_full5waves$surveyyear) # comparable
#table(df_full5waves$UrbanRuralInd, df_full5waves$surveyyear) # comparable
#table(df_full5waves$Country_DV, df_full5waves$surveyyear) # comparable
#table(df_full5waves$Q3_1, df_full5waves$surveyyear) # comparable responsability
#table(df_full5waves$Region_DV, df_full5waves$surveyyear) # comparable

#DEPENDANT VARIABLES
#table(df_full5waves$Q2_14s15_DV, df_full5waves$surveyyear) # comparable Consumption freq sandwich
#table(df_full5waves$Q2_14su7_DV, df_full5waves$surveyyear) # comparable Consumption freq diary
#table(df_full5waves$Q2_14su6_DV, df_full5waves$surveyyear) # comparable Consumption freq meat

#Label readability
#table(df_full5waves$Q6_4, df_full5waves$surveyyear) # comparable responsability

#INTERACTION VARIABLES
#table(df_full5waves$Q11_8b22, df_full5waves$surveyyear) # comparable get info on cooking safely, product packaging
#table(df_full5waves$Q11_8b25, df_full5waves$surveyyear) # comparable get info on cooking safely, dont seek 1=mentioned
#table(df_full5waves$Q4_27_6_Slice, df_full5waves$surveyyear) # comparable, worry about the food I have is safe to eat
#table(df_full5waves$bpoison, df_full5waves$surveyyear) # comparable
#table(df_full5waves$dietary, df_full5waves$surveyyear) # comparable few cases vegetarian/vegan
#table(df_full5waves$fdreac_dv, df_full5waves$surveyyear) # no comparable few cases avoid certain food

# Recode the variables 5 waves data set products
df_full5waves$Q2_14s15_DV[df_full5waves$Q2_14s15_dv %in% c(-1, 98, 9)] <- NA
df_full5waves$Q2_14su6_DV[df_full5waves$Q2_14su6_dv %in% c(-1, 98, 9)] <- NA
df_full5waves$Q2_14su6_DV[df_full5waves$Q2_14su7_DV %in% c(-1, 98, 9)] <- NA
df_full5waves$Q2_14su6_DV[df_full5waves$Q2_14sub_DV %in% c(-1, 98, 9)] <- NA

# Recode the variables 5 waves data set covariates
df_full5waves$bhhsize[df_full5waves$bhhsize == 5] <- 4 #recode own family size
df_full5waves$Age_Banded[df_full5waves$Age_Banded %in%c(5, 6, 7)] <- 1 #recode age
df_full5waves$age_dv[df_full5waves$age_dv %in%c(6, 7)] <- 6 #recode age
df_full5waves$Age_Banded[df_full5waves$Age_Banded == 8] <- 2 #recode age 
df_full5waves$Age_Banded[df_full5waves$Age_Banded == 9] <- 3 #recode age
df_full5waves$Age_Banded[df_full5waves$Age_Banded == 10] <- 4 #recode age
df_full5waves$Age_Banded[df_full5waves$Age_Banded == 11] <- 5 #recode age
df_full5waves$Age_Banded[df_full5waves$Age_Banded == 12] <- 6 #recode age
df_full5waves$age <- ifelse(!is.na(df_full5waves$age_dv) & df_full5waves$age_dv > 0, df_full5waves$age_dv,
                 ifelse(!is.na(df_full5waves$Age_Banded) & df_full5waves$Age_Banded > 0, df_full5waves$Age_Banded, NA))
table(df_full5waves$age, df_full5waves$surveyyear)
df_full5waves$Q3_1 <- as.numeric(as.character(df_full5waves$Q3_1))
df_full5waves <- df_full5waves %>%  
  mutate(Q3_1 = case_when(  
    Q3_1 %in% c(2, 3, 4, 5) ~ 2,#less than a half or nothing
    Q3_1 %in% c(1) ~ 1, 
    TRUE ~ NA_real_  
  )) 
table(df_full5waves$Q3_1, df_full5waves$surveyyear)


library(dplyr)

df_full5waves <- df_full5waves %>%  
  mutate(consumption_sandwich = case_when(  
    Q2_14s15_DV %in% c(1, 2, 3, 4) ~ 3,  #daily or weekly
    Q2_14s15_DV %in% c(5, 6, 7) ~ 2,  # monthly
    Q2_14s15_DV %in% c(8) ~ 1,  # never
    TRUE ~ NA_real_  
  )) 

df_full5waves <- df_full5waves %>%  
  mutate(consumption_precookedmeat = case_when(  
    Q2_14su6_DV %in% c(1, 2, 3,4) ~ 3, #daily and weekly 
    Q2_14su6_DV %in% c(5, 6, 7) ~ 2,  # monthly
    Q2_14su6_DV %in% c(8) ~ 1,  #never
    TRUE ~ NA_real_  
  )) 

df_full5waves <- df_full5waves %>%  
  mutate(consumption_sandwich_binary = case_when(  
    Q2_14s15_DV %in% c(1, 2, 3, 4, 5, 6, 7) ~ 1,  #daily or weekly
    Q2_14s15_DV %in% c(8) ~ 0,  # never
    TRUE ~ NA_real_  
  )) 

df_full5waves <- df_full5waves %>%  
  mutate(consumption_precookedmeat_binary = case_when(  
    Q2_14su6_DV %in% c(1, 2, 3,4, 5, 6, 7) ~ 1, #daily and weekly 
    Q2_14su6_DV %in% c(8) ~ 0,  #never
    TRUE ~ NA_real_  
  )) 

df_full5waves <- df_full5waves %>%  
  mutate(consumption_diary = case_when(  
    Q2_14su7_DV %in% c(1, 2, 3, 4) ~ 3,  #daily or weekly
    Q2_14su7_DV %in% c(5, 6, 7) ~ 2,  # monthly
    Q2_14su7_DV %in% c(8) ~ 1,  # never
    TRUE ~ NA_real_  
  )) 

df_full5waves <- df_full5waves %>%  
  mutate(consumption_meat = case_when(  
    Q2_14sub_DV %in% c(1, 2, 3, 4) ~ 3,  #daily or weekly
    Q2_14sub_DV %in% c(5, 6, 7) ~ 2,  # monthly
    Q2_14sub_DV %in% c(8) ~ 1,  # never
    TRUE ~ NA_real_  
  )) 

table(df_full5waves$consumption_sandwich, df_full5waves$surveyyear)
table(df_full5waves$consumption_precookedmeat, df_full5waves$surveyyear)
table(df_full5waves$consumption_diary, df_full5waves$surveyyear)
table(df_full5waves$consumption_meat, df_full5waves$surveyyear)


df_full5waves <- df_full5waves %>%  #antes era 1 very easy to read, ahora es very hard to read
  mutate(Q6_4 = case_when(  
    Q6_4 %in% c(5) ~ 1,  
    Q6_4 %in% c(4) ~ 2,  
    Q6_4 %in% c(3) ~ 3,  
    Q6_4 %in% c(2) ~ 4, 
    Q6_4 %in% c(1) ~ 5,  
    TRUE ~ NA_real_  
  )) 



```
## Recoding variables consumption frequence FSA df_full 5 waves

```{r table5, echo=FALSE}

library(writexl)

# Define key columns we consider essential  
key_columns2 <- c("SerialNo", "RespSex", "age", "below16", "bhhsize", "hhdinc", 
                 "marstat2", "Religion_DV", "UrbanRuralInd", "Country_DV",
                 "Q3_1", "Region_DV", "surveyyear", "psu_dv", "stratum_dv", 
                 "combinedW1_4weight", "consumption_precookedmeat", "consumption_sandwich", "consumption_diary","consumption_meat", "consumption_sandwich_binary", "consumption_precookedmeat_binary", 
                 "Q6_4", "Q11_8b25", "Q4_27_6_Slice")

# Subset the data to include only survey years 2, 3, 4, and 5
df_subset <- df_full5waves[df_full5waves$surveyyear %in% c(2, 3, 4, 5), key_columns2]


# Replace negative values and 98/99 with NA in all columns except SerialNo
for(col in names(df_subset)) {
    if(col != "SerialNo") {
        df_subset[[col]] <- ifelse(df_subset[[col]] < 0 | 
                                       df_subset[[col]] %in% c(98, 99), 
                                       NA, 
                                       df_subset[[col]])
    }
}

#COMPARABLE VARIABLES

#table(df_subset$RespSex, df_subset$surveyyear) #Comparable
#table(df_subset$age, df_subset$surveyyear) # comparable
#table(df_subset$below16, df_subset$surveyyear) # comparable
#table(df_subset$bhhsize, df_subset$surveyyear) # comparable
#table(df_subset$hhdinc, df_subset$surveyyear) # partially comparable recode
#table(df_subset$marstat2, df_subset$surveyyear) # comparable
#table(df_subset$religion_dv, df_subset$surveyyear) # comparable
#table(df_subset$UrbanRuralInd, df_subset$surveyyear) # comparable
#table(df_subset$country_dv, df_subset$surveyyear) # comparable
#table(df_subset$Q3_1, df_subset$surveyyear) # comparable responsability
#table(df_subset$Region_DV, df_subset$surveyyear) # comparable

#DEPENDANT VARIABLES
#table(df_subset$consumption_sandwich, df_subset$surveyyear) # comparable Consumption freq sandwich
#table(df_subset$consumption_precookedmeat, df_subset$surveyyear) # comparable Consumption freq meat

#Label readability
#table(df_subset$Q6_4, df_subset$surveyyear) # comparable responsability

#INTERACTION VARIABLES
#table(df_subset$Q11_8b22, df_subset$surveyyear) # comparable get info on cooking safely, product packaging
#table(df_subset$Q11_8b25, df_subset$surveyyear) # comparable get info on cooking safely, dont seek
#table(df_subset$bpoison, df_subset$surveyyear) # comparable

df_subset$Q4_27_6_Slice[df_subset$Q4_27_6_Slice == 6] <- NA
#table(df_subset$Q4_27_6_Slice, df_subset$surveyyear) # comparable, worry about the food I have is safe to eat

df_subset <- df_subset %>%
  mutate(read_level = case_when(
    Q6_4 <= 2 ~ "read_hard",
    Q6_4 == 3 ~ "read_medium",
    Q6_4 > 3  ~ "read_easy"
  )) %>%
  # Convert the new column to a factor
  mutate(read_level = as.factor(read_level))

df_subset <- df_subset %>%
  mutate(RespSex = case_when(
    RespSex == 1 ~ 1,  # Male remains 1
    RespSex == 2 ~ 0   # Female becomes 0
  ))

df_subset <- df_subset %>%
  mutate(below16 = case_when(
    below16 == 1 ~ 1,  # Yes remains 1
    below16 == 2 ~ 0   # No becomes 0
  ))

df_subset <- df_subset %>%
  mutate(marstat2 = case_when(
    marstat2 == 1 ~ 1,  # Married remains 1
    marstat2 == 2 ~ 0   # Single becomes 0
  ))

df_subset <- df_subset %>%
  mutate(UrbanRuralInd = case_when(
    UrbanRuralInd == 1 ~ 1,  # Urban remains 1
    UrbanRuralInd == 2 ~ 0   # Rural becomes 0
  ))



#subsets by year
df_subset2012 <- df_subset[df_subset$surveyyear == 2, ]
df_subset2014 <- df_subset[df_subset$surveyyear == 3, ]
df_subset2016 <- df_subset[df_subset$surveyyear == 4, ]
df_subset2018 <- df_subset[df_subset$surveyyear == 5, ]


# Export the data frame to an Excel file
write_xlsx(df_subset, path = "df_subset.xlsx")


```
## Checking multilinearity

The Variance Inflation Factor (VIF) measures how much the variance of a regression coefficient is inflated due to its correlation with other predictors in the model. Here's a breakdown of your results:

VIF Thresholds: A common rule of thumb is that VIF values:

Below 5 are considered acceptable.

Between 5 and 10 may be a cause for concern.

Above 10 indicate high multicollinearity that should be addressed.

Your Results: The highest VIF value in your model is for the bhhsize variable, at approximately 3.26. All other variables have VIF values well below this, with most being under 2.0.

```{r tableimpu, echo=FALSE}

#VIF test

library(foreign)
library(MASS)
library(Hmisc)
library(reshape2)
library(ordinal)
library(VGAM)
library(brant)

sv1 <- polr(factor(consumption_sandwich) ~ Q6_4 + RespSex + age + below16 + bhhsize + 
            + hhdinc + marstat2 + Religion_DV + UrbanRuralInd + Q3_1  
            + Country_DV+ surveyyear, 
                          data = df_subset, 
                          Hess = TRUE)
vif(sv1)




```

## Survey weights

```{r tableweight, echo=FALSE}

#Survey design
#When incorporating a complex survey design, always use the full dataset. Do not exclude any observations, not even to apply inclusion/exclusion criteria or to remove cases with missing data.
#we can tell R that we want the final analysis to apply only to a subgroup by creating a subpopulation indicator variable and subsetting the design (not the dataset) based on that variable at a later step.
#For example, we will subset on those with non-missing data, and we can also subset on those with positive weights.


# Complete case and positive weight indicator
         # (a vector of TRUE and FALSE values)
         nomiss <- complete.cases(df_subset[, c("SerialNo","RespSex", "age", "below16", "bhhsize",                  "hhdinc", "marstat2", "Religion_DV", "UrbanRuralInd", "Country_DV",
                 "Q3_1", "Region_DV", "surveyyear", "psu_dv", "stratum_dv", 
                 "combinedW1_4weight", "consumption_precookedmeat", "consumption_sandwich","consumption_diary", "consumption_meat",  
                 "Q6_4", "read_level", "Q11_8b25", "Q4_27_6_Slice")]) #CHECK THIS
         
# Create year indicators (if they don't exist already)
df_subset$year2012 <- df_subset$surveyyear == 2
df_subset$year2014 <- df_subset$surveyyear == 3
df_subset$year2016 <- df_subset$surveyyear == 4
df_subset$year2018 <- df_subset$surveyyear == 5

df_subset$hhdinc_group <- ifelse(df_subset$hhdinc %in% c("1", "2"), "Low income",
                         ifelse(df_subset$hhdinc %in% c("3", "4"), "High income", ""))
df_subset$lowincome <- df_subset$hhdinc_group == "Low income"
df_subset$highincome <- df_subset$hhdinc_group == "High income"

df_subset$infono <- df_subset$Q11_8b25 == 1
df_subset$infoyes <- df_subset$Q11_8b25 == 0

df_subset$eatsafe_group <- ifelse(df_subset$Q4_27_6_Slice %in% c("1", "2"), "High",
                         ifelse(df_subset$Q4_27_6_Slice %in% c("3", "4", "5"), "Low", ""))
df_subset$safehigh <- df_subset$eatsafe_group == "High"
df_subset$safelow <- df_subset$eatsafe_group == "Low"

library(svyVGAM)

options(survey.lonely.psu = "adjust") #specify how variance estimation will be handled in cases where a stratum contains only one PSU
options(survey.adjust.domain.lonely = TRUE) # specify how variance estimation will be handled in cases where a stratum contains only one PSU. These options “center the stratum at the population mean rather than the stratum mean” and make the same adjustment within subgroup analyses

survey_design <- svydesign(  
    id = ~psu_dv,  
    strata = ~stratum_dv,  
    weights = ~combinedW1_4weight,  
    data = df_subset,  
    nest = TRUE  
) 

#information of clusters and stratas
survey_design
summary(survey_design)

#create a design object to be used with analyses of cases with nomiss
#Filtering out cases with missing values is not actually necessary for the regression analysis itself but will ensure that the descriptive statistics and the regression analysis generalize to the same subpopulation.With survey_design.nomiss, descriptive statistics for all variables and the regression analysis all generalize to those in the population who would have had non-missing values for all the variables had they been sampled.
#There are 845 unique PSUs (Primary Sampling Units) in your dataset. However, the survey design summary reports 1,002 clusters. This discrepancy is due to the way the survey package in R handles the combination of PSUs and strata, especially when the nest = TRUE argument is used. When nest = TRUE, each PSU is considered within the context of its stratum, so the same PSU number in different strata is treated as a different cluster. This can increase the total number of clusters in the design object.
survey_design.nomiss <- subset(survey_design, nomiss)
survey_design.nomiss

#To avoid the problem that all years appear in the regression, create a new version of variable years with missing values at the excluded levels and use fct_drop() to drop the unused levels. This must be done before specifying and subsetting the design so that the new variable is available to the design.
# Set surveyyear2012 to NA for years 2, 3, 4 (so only 1 remain)
# Create survey designs for each year

# Create survey designs for each year
survey_design.2012 <- subset(survey_design.nomiss, year2012)
survey_design.2014 <- subset(survey_design.nomiss, year2014)
survey_design.2016 <- subset(survey_design.nomiss, year2016)
survey_design.2018 <- subset(survey_design.nomiss, year2018)

survey_design.lowincome <- subset(survey_design.nomiss, lowincome)
survey_design.highincome <- subset(survey_design.nomiss, highincome)

survey_design.infono <- subset(survey_design.nomiss, infono)
survey_design.infoyes <- subset(survey_design.nomiss, infoyes)

survey_design.safehigh <- subset(survey_design.nomiss, safehigh)
survey_design.safelow <- subset(survey_design.nomiss, safelow)

#statistics readability
# Weighted mean, standard deviation, and 95% CI
cbind(
 "readMEAN" = svymean(~Q6_4, survey_design.nomiss),
 "readSD"   = sqrt(svyvar(~Q6_4, survey_design.nomiss)[1]),
       confint(svymean(~Q6_4, survey_design.nomiss), df=degf(survey_design.nomiss))
)


```

## Ordinal logistic regression FSA df_full 2012-2018 -  no proportional odds weighted Sandwich and precooked meat + general


```{r tablegen, echo=FALSE}


gen0a <- svy_vglm(
  consumption_sandwich ~ Q6_4,
  family = cumulative(parallel = FALSE),
  design = survey_design.nomiss)

summary(gen0a)

gen1 <- svy_vglm(
  consumption_sandwich ~ Q6_4 + RespSex + age + Religion_DV + hhdinc_group + UrbanRuralInd + Q3_1  + below16 + Country_DV,
  family = cumulative(parallel = ~ Religion_DV + Q3_1 + Country_DV),
  design = survey_design.nomiss)

summary(gen1)

# Show all coefficients in the model  
print(coef(gen1))  

gen2 <- svy_vglm(
  consumption_sandwich ~ Q6_4*factor(surveyyear) + RespSex + age + Religion_DV + hhdinc_group + UrbanRuralInd + Q3_1  + below16 + Country_DV,
  family = cumulative(parallel = ~ Religion_DV + Q3_1 + Country_DV),
  design = survey_design.nomiss)

summary(gen2)

gen0b <- svy_vglm(
  consumption_precookedmeat ~ Q6_4,
  family = cumulative(parallel = FALSE),
  design = survey_design.nomiss)

summary(gen0b)

gen3 <- svy_vglm(
  consumption_precookedmeat ~ Q6_4 + RespSex + age + Religion_DV + hhdinc_group + UrbanRuralInd + Q3_1  + below16 + Country_DV,
  family = cumulative(parallel = ~ Religion_DV + Q3_1 + Country_DV),
  design = survey_design.nomiss)

summary(gen3)

gen4 <- svy_vglm(
  consumption_precookedmeat ~ Q6_4*surveyyear + RespSex + age + Religion_DV + hhdinc_group + UrbanRuralInd + Q3_1  + below16 + Country_DV,
  family = cumulative(parallel = ~ Religion_DV + Q3_1+ Country_DV),
  design = survey_design.nomiss)

summary(gen4)

```

## Brant test

The Brant test checks the proportional odds assumption (also called the parallel regression assumption). This assumption is crucial for ordinal logistic regression. It implies that the effect of each predictor variable is the same across all cumulative splits of your ordinal outcome variable (e.g., the effect of age is the same when comparing 'level 1' vs 'levels 2 & 3' as it is when comparing 'levels 1 & 2' vs 'level 3').

The null hypothesis (H0 ) for the Brant test is that the proportional odds assumption holds. A small p-value (typically < 0.05) provides evidence to reject the null hypothesis, indicating that the assumption is violated.

Variables that VIOLATE the assumption (p < 0.05):
These variables have an inconsistent effect across the different levels of your outcome variable.

RespSex: p ≈ 0

age: p ≈ 0

hhdinc_groupHigh income: p = 0.00038

UrbanRuralInd: p = 0.00337

surveyyear: p = 0.000029

readability does not violate the parallel assumption as continous o categorical variable

No moy diferente el uno del otro.

```{r brant, echo=FALSE}

library(stargazer)
library(foreign)
library(ggplot2)
library(MASS)
library(Hmisc)
library(reshape2)
library(ordinal)
library(VGAM)
library(brant)

sv1 <- polr(factor(consumption_sandwich) ~  Q6_4 + RespSex + age + Religion_DV + hhdinc_group + UrbanRuralInd + Q3_1  + below16 + bhhsize + marstat2 + Country_DV + surveyyear, 
                          data = df_subset, 
                          Hess = TRUE)
summary(sv1)

#The Brant test for the proportional odds assumption should be conducted on an unweighted model because it's not directly compatible with survey-weighted models. 
brant_results <- brant(sv1)
print(brant_results)

sv2 <- polr(factor(consumption_precookedmeat) ~  Q6_4 + RespSex + age + Religion_DV + hhdinc_group + UrbanRuralInd + Q3_1  + below16 + bhhsize + marstat2 + Country_DV + surveyyear, 
                          data = df_subset, 
                          Hess = TRUE)
summary(sv2)

#The Brant test for the proportional odds assumption should be conducted on an unweighted model because it's not directly compatible with survey-weighted models. 
brant_results2 <- brant(sv2)
print(brant_results2)

sv3 <- polr(factor(consumption_diary) ~  Q6_4 + RespSex + age + Religion_DV + hhdinc_group + UrbanRuralInd + Q3_1 + below16 + bhhsize + marstat2 + Country_DV + surveyyear, 
                          data = df_subset, 
                          Hess = TRUE)
summary(sv3)

#The Brant test for the proportional odds assumption should be conducted on an unweighted model because it's not directly compatible with survey-weighted models. 
brant_results3 <- brant(sv3)
print(brant_results3)

sv4 <- polr(factor(consumption_meat) ~  Q6_4 + RespSex + age + Religion_DV + hhdinc_group + UrbanRuralInd + Q3_1  + below16 + bhhsize + marstat2 + Country_DV + surveyyear, 
                          data = df_subset, 
                          Hess = TRUE)
summary(sv4)

#The Brant test for the proportional odds assumption should be conducted on an unweighted model because it's not directly compatible with survey-weighted models. 
brant_results4 <- brant(sv4)
print(brant_results4)


```

## Ordinal logistic regression FSA df_full 2012-2018 -  no proportional odds weighted Sandwich and precooked meat + readability proportional odd PUBLICATION

```{r reada, echo=FALSE}


gen11 <- svy_vglm(
  consumption_sandwich ~ Q6_4 + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV) + factor(surveyyear),
  family = cumulative(parallel = ~ Q6_4 + factor(Religion_DV) + hhdinc_group + below16 + marstat2 + factor(Country_DV)),
  design = survey_design.nomiss
)
summary(gen11)


gen22 <- svy_vglm(
  consumption_sandwich ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = ~  Q6_4 + factor(Religion_DV) + hhdinc_group + below16 + marstat2 + factor(Country_DV) + Q6_4*factor(surveyyear)),
  design = survey_design.nomiss)

summary(gen22)

gen33 <- svy_vglm(consumption_precookedmeat ~ Q6_4 + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + Country_DV + factor(surveyyear),
  family = cumulative(parallel = ~ Q6_4 + RespSex + age + factor(Religion_DV) + UrbanRuralInd + below16 + marstat2 + Q3_1 + Country_DV),
  design = survey_design.nomiss)

summary(gen33)

gen44 <- svy_vglm(
  consumption_precookedmeat ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = ~  Q6_4 + RespSex + age + factor(Religion_DV) + UrbanRuralInd + below16 + marstat2 + Q3_1 + factor(Country_DV) + Q6_4*factor(surveyyear)),
  design = survey_design.nomiss)

summary(gen44)


```
## Ordinal logistic regression FSA df_full 2012-2018 -  no proportional odds weighted Sandwich and precooked meat + readability proportional odd PLOTs

```{r reada2, echo=FALSE}

# install.packages("ggplot2") # Run this line if you don't have ggplot2 installed
# install.packages("patchwork") # Run this to arrange plots together
library(ggplot2)
library(patchwork)

# ==============================================================================
# PLOT 1: SANDWICH CONSUMPTION (ODDS RATIOS)
# ==============================================================================

# --- Step 1a: Define Coefficients from the NEW Sandwich Consumption Model ---
# (Using exact values from R output)
b_q6_4_sandwich <- -0.097686
b_q6_4_yr_2014_sandwich <- 0.061022
b_q6_4_yr_2016_sandwich <- 0.052750
b_q6_4_yr_2018_sandwich <- 0.139325

# --- Step 2a: Calculate the Marginal Effect (Log-Odds) for Each Year ---
effect_yr_2012_sandwich <- b_q6_4_sandwich
effect_yr_2014_sandwich <- b_q6_4_sandwich + b_q6_4_yr_2014_sandwich
effect_yr_2016_sandwich <- b_q6_4_sandwich + b_q6_4_yr_2016_sandwich
effect_yr_2018_sandwich <- b_q6_4_sandwich + b_q6_4_yr_2018_sandwich

# --- Step 3a: Create a Data Frame and Convert Effects to Odds Ratios ---
plot_data_sandwich <- data.frame(
  Year = c(2012, 2014, 2016, 2018),
  Effect = c(effect_yr_2012_sandwich, effect_yr_2014_sandwich, effect_yr_2016_sandwich, effect_yr_2018_sandwich)
)
plot_data_sandwich$OddsRatio <- exp(plot_data_sandwich$Effect)

# ==============================================================================
# PLOT 2: PRE-COOKED MEAT CONSUMPTION (ODDS RATIOS)
# ==============================================================================

# --- Step 1b: Define Coefficients from the NEW Pre-cooked Meat Model ---
# (Using exact values from R output)
b_q6_4_meat <- 0.0261802
b_q6_4_yr_2014_meat <- -0.0319737
b_q6_4_yr_2016_meat <- -0.0748803
b_q6_4_yr_2018_meat <- -0.0191249

# --- Step 2b: Calculate the Marginal Effect (Log-Odds) for Each Year ---
effect_yr_2012_meat <- b_q6_4_meat
effect_yr_2014_meat <- b_q6_4_meat + b_q6_4_yr_2014_meat
effect_yr_2016_meat <- b_q6_4_meat + b_q6_4_yr_2016_meat
effect_yr_2018_meat <- b_q6_4_meat + b_q6_4_yr_2018_meat

# --- Step 3b: Create a Data Frame and Convert Effects to Odds Ratios ---
plot_data_meat <- data.frame(
  Year = c(2012, 2014, 2016, 2018),
  Effect = c(effect_yr_2012_meat, effect_yr_2014_meat, effect_yr_2016_meat, effect_yr_2018_meat)
)
plot_data_meat$OddsRatio <- exp(plot_data_meat$Effect)

# ==============================================================================
# PLOT 3: DAIRY (NEDV) (ODDS RATIOS)
# ==============================================================================

# --- Step 1c: Define Coefficients from the NEW Dairy Model ---
# (Using exact values from R output)
b_q6_4_diary <- -0.0700570
b_q6_4_yr_2014_diary <- 0.0365404
b_q6_4_yr_2016_diary <- 0.1027693
b_q6_4_yr_2018_diary <- 0.1347710

# --- Step 2c: Calculate the Marginal Effect (Log-Odds) for Each Year ---
effect_yr_2012_diary <- b_q6_4_diary
effect_yr_2014_diary <- b_q6_4_diary + b_q6_4_yr_2014_diary
effect_yr_2016_diary <- b_q6_4_diary + b_q6_4_yr_2016_diary
effect_yr_2018_diary <- b_q6_4_diary + b_q6_4_yr_2018_diary

# --- Step 3c: Create a Data Frame and Convert Effects to Odds Ratios ---
plot_data_diary <- data.frame(
  Year = c(2012, 2014, 2016, 2018),
  Effect = c(effect_yr_2012_diary, effect_yr_2014_diary, effect_yr_2016_diary, effect_yr_2018_diary)
)
plot_data_diary$OddsRatio <- exp(plot_data_diary$Effect)

# ==============================================================================
# PLOT 4: FRESH MEAT (NEDV) (ODDS RATIOS)
# ==============================================================================

# --- Step 1d: Define Coefficients from the NEW Fresh Meat Model ---
# (Using exact values from R output)
b_q6_4_fresh_meat <- 0.0464171
b_q6_4_yr_2014_fresh_meat <- -0.0811353
b_q6_4_yr_2016_fresh_meat <- -0.0279599
b_q6_4_yr_2018_fresh_meat <- 0.0029789

# --- Step 2d: Calculate the Marginal Effect (Log-Odds) for Each Year ---
effect_yr_2012_fresh_meat <- b_q6_4_fresh_meat
effect_yr_2014_fresh_meat <- b_q6_4_fresh_meat + b_q6_4_yr_2014_fresh_meat
effect_yr_2016_fresh_meat <- b_q6_4_fresh_meat + b_q6_4_yr_2016_fresh_meat
effect_yr_2018_fresh_meat <- b_q6_4_fresh_meat + b_q6_4_yr_2018_fresh_meat

# --- Step 3d: Create a Data Frame and Convert Effects to Odds Ratios ---
plot_data_fresh_meat <- data.frame(
  Year = c(2012, 2014, 2016, 2018),
  Effect = c(effect_yr_2012_fresh_meat, effect_yr_2014_fresh_meat, effect_yr_2016_fresh_meat, effect_yr_2018_fresh_meat)
)
plot_data_fresh_meat$OddsRatio <- exp(plot_data_fresh_meat$Effect)

# ==============================================================================
# PLOTTING
# ==============================================================================

# --- Step 4: Set a common Y-axis scale for ALL FOUR plots ---
min_or <- min(plot_data_sandwich$OddsRatio, plot_data_meat$OddsRatio, 
              plot_data_diary$OddsRatio, plot_data_fresh_meat$OddsRatio)
max_or <- max(plot_data_sandwich$OddsRatio, plot_data_meat$OddsRatio, 
              plot_data_diary$OddsRatio, plot_data_fresh_meat$OddsRatio)
# Add a little padding
y_axis_limits <- c(floor(min_or * 10) / 10, ceiling(max_or * 10) / 10)


# --- Step 5a: Create the Greyscale Plot (Sandwich) ---
plot_sandwich <- ggplot(plot_data_sandwich, aes(x = Year, y = OddsRatio)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray50") +
  geom_line(aes(group = 1), color = "black", size = 1) +
  geom_point(color = "black", size = 4) +
  scale_y_continuous(limits = y_axis_limits) +
  scale_x_continuous(breaks = c(2012, 2014, 2016, 2018)) +
  labs(
    title = "A) Pre-package sandwich",
    subtitle = "(Labeled)",
    x = "Year",
    y = "Odds Ratio"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )

# --- Step 5b: Create the Greyscale Plot (Meat) ---
plot_meat <- ggplot(plot_data_meat, aes(x = Year, y = OddsRatio)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray50") +
  geom_line(aes(group = 1), color = "black", size = 1) +
  geom_point(color = "black", size = 4) +
  scale_y_continuous(limits = y_axis_limits) +
  scale_x_continuous(breaks = c(2012, 2014, 2016, 2018)) +
  labs(
    title = "B) Pre-cooked Meat",
    subtitle = "(Labeled)",
    x = "Year",
    y = "Odds Ratio"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )

# --- Step 5c: Create the Greyscale Plot (Diary) ---
plot_diary <- ggplot(plot_data_diary, aes(x = Year, y = OddsRatio)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray50") +
  geom_line(aes(group = 1), color = "black", size = 1) +
  geom_point(color = "black", size = 4) +
  scale_y_continuous(limits = y_axis_limits) +
  scale_x_continuous(breaks = c(2012, 2014, 2016, 2018)) +
  labs(
    title = "C) Dairy",
    subtitle = "(Labeled)",
    x = "Year",
    y = "Odds Ratio"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )

# --- Step 5d: Create the Greyscale Plot (Fresh Meat) ---
plot_fresh_meat <- ggplot(plot_data_fresh_meat, aes(x = Year, y = OddsRatio)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray50") +
  geom_line(aes(group = 1), color = "black", size = 1) +
  geom_point(color = "black", size = 4) +
  scale_y_continuous(limits = y_axis_limits) +
  scale_x_continuous(breaks = c(2012, 2014, 2016, 2018)) +
  labs(
    title = "D) Fresh Meat",
    subtitle = "(No Label)",
    x = "Year",
    y = "Odds Ratio"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )

# --- Step 6: Combine plots into a 2x2 grid and export ---
# (plot1 + plot2) is the top row, (plot3 + plot4) is the bottom row
combined_plot <- (plot_sandwich + plot_meat) / (plot_diary + plot_fresh_meat)

print(combined_plot)

# Save as a square plot (12 width, 12 height)
ggsave("interaction_plots_2x2_updated.png", combined_plot, width = 12, height = 12, dpi = 300)


```

## Ordinal logistic regression FSA df_full 2012-2018 -  no proportional odds weighted Sandwich and precooked meat + Income groups

I need to impute the values

```{r table16, echo=FALSE}

inc1 <- svy_vglm(
  consumption_sandwich ~ Q6_4*factor(surveyyear) + 
    RespSex + age + Religion_DV + UrbanRuralInd + Q3_1 + 
    below16 + Country_DV,
  family = cumulative(parallel = ~ Q6_4 + Religion_DV + hhdinc_group + below16 + Country_DV+Q6_4*factor(surveyyear)),
  design = survey_design.lowincome)

summary(inc1)


inc2 <- svy_vglm(consumption_sandwich ~ Q6_4*factor(surveyyear) + 
    RespSex + age + Religion_DV + UrbanRuralInd + Q3_1 + 
    below16 + Country_DV,
  family = cumulative(parallel = ~ Religion_DV + Q3_1 + Country_DV+Q6_4*factor(surveyyear)),
  design = survey_design.highincome)

summary(inc2)

inc4 <- svy_vglm(consumption_precookedmeat ~ Q6_4*factor(surveyyear)+ 
    RespSex + age + Religion_DV + UrbanRuralInd + Q3_1 + 
    below16 + Country_DV,
  family = cumulative(parallel = ~ Religion_DV + Q3_1 + Country_DV+Q6_4*factor(surveyyear)),
  design = survey_design.lowincome)

summary(inc4)

inc5 <- svy_vglm(consumption_precookedmeat ~ Q6_4*factor(surveyyear)+ 
    RespSex + age + Religion_DV + UrbanRuralInd + Q3_1 + 
    below16 + Country_DV,
  family = cumulative(parallel = ~ Religion_DV + Q3_1 + Country_DV+Q6_4*factor(surveyyear)),
  design = survey_design.highincome)

summary(inc5)

```

## Ordinal logistic regression FSA df_full 2012-2018 -  no proportional odds weighted Sandwich and precooked meat + info seeking

I need to impute the values

```{r table18, echo=FALSE}

inc11 <- svy_vglm(
  consumption_sandwich ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel =  TRUE),
  design = survey_design.infono)

summary(inc11)


inc12 <- svy_vglm(
  consumption_sandwich ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = TRUE),
  design = survey_design.infoyes)

summary(inc12)


  inc13 <- svy_vglm(
    consumption_precookedmeat ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
    family = cumulative(parallel = TRUE),
    design = survey_design.infono)
    
  summary(inc13)
  
  inc14 <- svy_vglm(consumption_precookedmeat ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
    family = cumulative(parallel = TRUE),
    design = survey_design.infoyes)
  
  summary(inc14)
  
  
  inc11a <- svy_vglm(
  consumption_diary ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = TRUE),
  design = survey_design.infono)

summary(inc11a)


inc12a <- svy_vglm(
  consumption_diary ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = TRUE),
  design = survey_design.infoyes)

summary(inc12a)


  inc13a <- svy_vglm(
    consumption_meat ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
    family = cumulative(parallel = TRUE),
    design = survey_design.infono)
    
  summary(inc13a)
  
  inc14a <- svy_vglm(consumption_meat ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
    family = cumulative(parallel = TRUE),
    design = survey_design.infoyes)
  
  summary(inc14a)
  
  


```

## Ordinal logistic regression FSA df_full 2012-2018 -  no proportional odds weighted Sandwich and precooked meat + eat safely

I need to impute the values

```{r table19, echo=FALSE}

# A simpler model that is more likely to run on a subset
inc15 <- svy_vglm(
  consumption_sandwich ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV) + factor(surveyyear),
  family = cumulative(parallel = ~ Q6_4 + factor(Religion_DV) + hhdinc_group + below16 + marstat2 + factor(Country_DV) + Q6_4*factor(surveyyear)),
  design = survey_design.safehigh
)


summary(inc15)

inc16 <- svy_vglm(
  consumption_sandwich ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV) + factor(surveyyear),
  family = cumulative(parallel = ~ Q6_4 + factor(Religion_DV) + hhdinc_group + below16 + marstat2 + factor(Country_DV) + Q6_4*factor(surveyyear)),
  design = survey_design.safelow
)

summary(inc16)


inc18 <- svy_vglm(consumption_precookedmeat ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = ~  Q6_4 + RespSex + age + factor(Religion_DV) + factor(UrbanRuralInd) + below16 + marstat2 + Q3_1 + factor(Country_DV) + Q6_4*factor(surveyyear)),
  design = survey_design.safehigh)

summary(inc18)

inc20 <- svy_vglm(consumption_precookedmeat ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = ~  Q6_4 + RespSex + age + factor(Religion_DV) + factor(UrbanRuralInd) + below16 + marstat2 + Q3_1 + factor(Country_DV) + Q6_4*factor(surveyyear)),
  design = survey_design.safelow)

summary(inc20)

inc15a <- svy_vglm(
  consumption_diary ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV) + factor(surveyyear),
  family = cumulative(parallel = TRUE),
  design = survey_design.safehigh
)


summary(inc15a)

inc16a <- svy_vglm(
  consumption_diary ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV) + factor(surveyyear),
  family = cumulative(parallel = TRUE),
  design = survey_design.safelow
)

summary(inc16a)


inc18a <- svy_vglm(consumption_meat ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = ~  Q6_4 + RespSex + age + factor(Religion_DV) + factor(UrbanRuralInd) + below16 + marstat2 + Q3_1 + factor(Country_DV) + Q6_4*factor(surveyyear)),
  design = survey_design.safehigh)

summary(inc18a)

inc20a <- svy_vglm(consumption_meat ~ Q6_4*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + factor(UrbanRuralInd) + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = TRUE),
  design = survey_design.safelow)

summary(inc20a)

```


## Sociodemographic variables table weighted Sandwich

```{r sociow, echo=FALSE}


# Load necessary libraries
library(survey)
library(xtable)

# First, ensure the survey design object is created
# This code assumes 'survey_design.nomiss' already exists from your model script.

# --- 1. MODIFIED HELPER FUNCTION (Outputs Percentages Only) ---
# This function now handles cases where a consumption level might be missing.
create_weighted_demo_table <- function(variable, categories, outcome_var) {
  
  # The formula now uses the specified outcome variable
  formula_str <- paste("~", variable, "+", outcome_var)
  
  # Ensure the variables exist and have data
  if (!variable %in% names(survey_design.nomiss$variables) || 
      !outcome_var %in% names(survey_design.nomiss$variables)) {
    stop(paste("Variable", variable, "or", outcome_var, "not found in survey design."))
  }
  
  tab <- svytable(as.formula(formula_str), survey_design.nomiss)
  
  # Calculate column percentages
  prop_tab <- prop.table(tab, margin = 2) * 100
  
  # --- ROBUSTNESS FIX START ---
  # Create a placeholder for all possible consumption levels
  all_consumption_levels <- c("1", "2", "3")
  
  # Create a full matrix to store results, ensuring it always has 3 columns
  # MODIFIED: Placeholder is now "0.0" for percentage only
  full_result_matrix <- matrix("0.0", nrow = nrow(tab), ncol = length(all_consumption_levels))
  colnames(full_result_matrix) <- c("Never", "Monthly", "Weekly") # Use desired names
  
  # Get the names of the levels that actually exist in the current table
  existing_levels <- colnames(tab)
  
  # Fill the full matrix with data from the existing levels
  for (i in 1:nrow(tab)) {
    for (level in existing_levels) {
      # Find the correct column index in our full matrix
      col_idx <- which(all_consumption_levels == level)
      if (length(col_idx) > 0) {
        # Get the corresponding column from the original table
        original_col_idx <- which(colnames(tab) == level)
        
        # MODIFIED: Format to be percentage only (e.g., "25.1")
        full_result_matrix[i, col_idx] <- sprintf("%.1f", prop_tab[i, original_col_idx])
      }
    }
  }
  # --- ROBUSTNESS FIX END ---
  
  # Ensure category labels match the number of rows
  actual_categories <- nrow(tab)
  if(length(categories) != actual_categories) {
    categories <- categories[1:actual_categories]
  }
  
  # Convert to a data frame
  result_df <- as.data.frame(full_result_matrix)
  
  # Add the variable and category labels for the final table structure
  result_df$Category <- categories
  result_df$Variable <- c(variable, rep("", nrow(result_df)-1))
  
  # Reorder columns for the final output
  result_df <- result_df[, c("Variable", "Category", "Never", "Monthly", "Weekly")]
  
  return(result_df)
}

# --- 2. UNCHANGED FUNCTION DEFINITION ---
# This function correctly accepts 'outcome_var' and passes it to the helper function.
create_full_demo_table <- function(outcome_var) {
  sex_table <- create_weighted_demo_table("RespSex", c("Male", "Female"), outcome_var)
  age_table <- create_weighted_demo_table("age", c("16-24", "25-34", "35-44", "45-54", "55-64", "65+"), outcome_var)
  income_table <- create_weighted_demo_table("hhdinc_group", c("Low income", "High income"), outcome_var)
  size_table <- create_weighted_demo_table("bhhsize", c("1", "2", "3", "4"), outcome_var)
  marital_table <- create_weighted_demo_table("marstat2", c("Married/Similar", "Single/Similar"), outcome_var)
  religion_table <- create_weighted_demo_table("Religion_DV", c("Christian", "Other religion", "No religion"), outcome_var)
  children_table <- create_weighted_demo_table("below16", c("Yes", "No"), outcome_var)
  responsability_table <- create_weighted_demo_table("Q3_1", c("All/Most", "Sometimes/Never"), outcome_var)
  area_table <- create_weighted_demo_table("UrbanRuralInd", c("Urban", "Rural"), outcome_var)
  country_table <- create_weighted_demo_table("Country_DV", c("England", "Wales", "Northern Ireland"), outcome_var)
  years_table <- create_weighted_demo_table("surveyyear", c("2012", "2014", "2016", "2018"), outcome_var)
  # Assuming 'eatsafe_group' and 'Q11_8b25' are your variable names.
  eatsafe_table <- create_weighted_demo_table("eatsafe_group", c("High", "Low"), outcome_var)
  infoseek_table <- create_weighted_demo_table("Q11_8b25", c("Yes", "No"), outcome_var)
  
  full_table <- rbind(sex_table, age_table, income_table, size_table, marital_table, religion_table, children_table, responsability_table, area_table, country_table, years_table, eatsafe_table, infoseek_table)
  return(full_table)
}

# ==============================================================================
# 3. NEW: GET COLUMN N's (The "number for the full table")
# ==============================================================================
# This calculates the unweighted N for each consumption level.
# You will MANUALLY add these numbers to your LaTeX table header.

print("--- UNWEIGHTED COLUMN Ns (Manually add to LaTeX header) ---")
print(paste("Total N in 'survey_design.nomiss':", nrow(survey_design.nomiss$variables)))

print("--- consumption_sandwich ---")
print(table(survey_design.nomiss$variables$consumption_sandwich))

print("--- consumption_precookedmeat ---")
print(table(survey_design.nomiss$variables$consumption_precookedmeat))

print("--- consumption_diary (NEDV) ---")
print(table(survey_design.nomiss$variables$consumption_diary))

print("--- consumption_meat (NEDV) ---")
print(table(survey_design.nomiss$variables$consumption_meat))


# ==============================================================================
# 4. MODIFIED: GENERATE AND COMBINE ALL FOUR TABLES
# ==============================================================================

# --- Generate the four separate tables first ---
demo_table_sandwich <- create_full_demo_table("consumption_sandwich")
demo_table_meat <- create_full_demo_table("consumption_precookedmeat")
demo_table_diary <- create_full_demo_table("consumption_diary")
demo_table_meat_falsify <- create_full_demo_table("consumption_meat") # NEDV


# --- Combine them into a single data frame ---
# Create the first column with merged Variable/Category
row_labels_vec <- ifelse(demo_table_sandwich$Variable != "", 
                         as.character(demo_table_sandwich$Variable), 
                         paste("  ", demo_table_sandwich$Category)) # Indent categories
row_labels_df <- data.frame(Category = row_labels_vec)

# MODIFIED: Combine all 4 tables (12 columns)
combined_data <- cbind(
  demo_table_sandwich[, c("Never", "Monthly", "Weekly")],
  demo_table_meat[, c("Never", "Monthly", "Weekly")],
  demo_table_diary[, c("Never", "Monthly", "Weekly")],
  demo_table_meat_falsify[, c("Never", "Monthly", "Weekly")]
)

# Create the final, wide data frame
final_combined_table <- cbind(row_labels_df, combined_data)


# ==============================================================================
# 5. MODIFIED: Create the LaTeX table with 4-product headers
# ==============================================================================

print('--- Combined Demographic Table (Percentages Only) ---')
print(final_combined_table)

# MODIFIED: New 4-product, 12-column header
header_command <- paste(
  "\\toprule & \\multicolumn{3}{c}{Pre-package Sandwich} &",
  "\\multicolumn{3}{c}{Pre-cooked Meat} &",
  "\\multicolumn{3}{c}{Dairy (NEDV)} &",
  "\\multicolumn{3}{c}{Fresh Meat (NEDV)} \\\\",
  "\\cmidrule(lr){2-4} \\cmidrule(lr){5-7} \\cmidrule(lr){8-10} \\cmidrule(lr){11-13}"
)

# Create the xtable object
latex_combined_table <- xtable(final_combined_table,
                               caption = 'Weighted Demographic Characteristics by Consumption Frequency (Percentages Only)',
                               label = 'tab:demographics_combined_pct')

# MODIFIED: New 13-column names
names(latex_combined_table) <- c("Category", 
                                 "Never", "Monthly", "Weekly", 
                                 "Never", "Monthly", "Weekly", 
                                 "Never", "Monthly", "Weekly", 
                                 "Never", "Monthly", "Weekly")


# Print the final LaTeX code
print('--- LaTeX Code for Combined Table (Percentages Only) ---')
print(latex_combined_table,
      include.rownames = FALSE,
      caption.placement = 'top',
      sanitize.text.function = identity,
      booktabs = TRUE,
      add.to.row = list(pos = list(-1), command = header_command),
      table.placement = "htbp",
      size = "\\small"
)



```

## Readability mean table weighted

```{r table20, echo=FALSE}


library(survey)
library(xtable)

# This code assumes 'survey_design.nomiss' and 'df_subset' exist from your previous scripts.
# NOTE: This function's logic is from your original file.
# It calculates Mean (SE) of Q6_4, broken down by a variable AND by year.

# --- 1. Function to create weighted mean (SE) tables ---
create_weighted_mean_se_table <- function(variable, categories) {
  # This part of your code assumes 'surveyyear' and 'Q6_4' are in the design
  
  years <- c(2, 3, 4, 5) # Assuming these are your year codes
  year_labels <- c("2012", "2014", "2016", "2018")
  
  # Get unique codes for the variable
  codes <- unique(df_subset[[variable]])
  codes <- codes[codes != ""] # Remove empty string if present
  
  # If categories are named, match codes to categories
  if(length(categories) != length(codes)) {
    categories <- categories[1:length(codes)]
  }
  
  result_matrix <- matrix(NA, nrow = length(codes), ncol = length(years))
  se_matrix <- matrix(NA, nrow = length(codes), ncol = length(years))
  
  for(i in seq_along(codes)) {
    for(j in seq_along(years)) {
      # Subset for non-missing values
      subset_design <- subset(survey_design.nomiss, !is.na(get(variable)) & !is.na(Q6_4) & get(variable) == codes[i] & surveyyear == years[j])
      
      if (length(subset_design$variables[[1]]) > 0) {
        mean_result <- svymean(~Q6_4, subset_design, na.rm = TRUE)
        result_matrix[i, j] <- as.numeric(mean_result)
        se_matrix[i, j] <- as.numeric(SE(mean_result))
      } else {
        result_matrix[i, j] <- NA
        se_matrix[i, j] <- NA
      }
    }
  }
  
  # Combine mean and SE as "mean (SE)"
  combined_matrix <- matrix(NA, nrow = length(codes), ncol = length(years))
  for (i in seq_along(codes)) {
    for (j in seq_along(years)) {
      if (!is.na(result_matrix[i, j])) {
        combined_matrix[i, j] <- sprintf("%.2f (%.2f)", result_matrix[i, j], se_matrix[i, j])
      } else {
        combined_matrix[i, j] <- NA
      }
    }
  }
  
  result_df <- as.data.frame(combined_matrix)
  colnames(result_df) <- year_labels
  result_df$Category <- categories
  result_df$Variable <- c(variable, rep("", length(categories) - 1))
  result_df <- result_df[, c("Variable", "Category", "2012", "2014", "2016", "2018")]
  return(result_df)
}

# --- 2. Define ALL labels (Old and New) ---
sex_labels <- c("Male", "Female")
age_labels <- c("16-24", "25-34", "35-44", "45-54", "55-64", "65+")
income_labels <- c("Low income", "High income")
religion_labels <- c("Christian", "Other religion", "No religion")
urban_labels <- c("Urban", "Rural")
children_labels <- c("Yes", "No")
responsability_labels <- c("All/Most", "Sometimes/Never")
country_labels <- c("England", "Wales", "Northern Ireland")
eatsafe_group_labels <- c("High", "Low")
infoseeking_labels <- c("1", "0")
sandwich_labels <- c("Never", "Monthly", "Weekly")
meat_labels <- c("Never", "Monthly", "Weekly")
# --- NEW LABELS ---
diary_labels <- c("Never", "Monthly", "Weekly")
fresh_meat_labels <- c("Never", "Monthly", "Weekly")


# --- 3. Run the function for all variables ---
age_mean_se_table <- create_weighted_mean_se_table("age", age_labels)
income_mean_se_table <- create_weighted_mean_se_table("hhdinc_group", income_labels)
religion_mean_se_table <- create_weighted_mean_se_table("Religion_DV", religion_labels)
urban_mean_se_table <- create_weighted_mean_se_table("UrbanRuralInd", urban_labels)
children_mean_se_table <- create_weighted_mean_se_table("below16", children_labels)
responsability_mean_se_table <- create_weighted_mean_se_table("Q3_1", responsability_labels)
country_mean_se_table <- create_weighted_mean_se_table("Country_DV", country_labels)
eatsafe_group_mean_se_table <- create_weighted_mean_se_table("eatsafe_group", eatsafe_group_labels)
infoseeking_mean_se_table <- create_weighted_mean_se_table("Q11_8b25", infoseeking_labels)
sex_mean_se_table <- create_weighted_mean_se_table("RespSex", sex_labels)

# Product variables (Old)
sandwich_mean_se_table <- create_weighted_mean_se_table("consumption_sandwich", sandwich_labels)
meat_mean_se_table <- create_weighted_mean_se_table("consumption_precookedmeat", meat_labels)

# --- NEW PRODUCT CALLS ---
diary_mean_se_table <- create_weighted_mean_se_table("consumption_diary", diary_labels)
fresh_meat_mean_se_table <- create_weighted_mean_se_table("consumption_meat", fresh_meat_labels)


# --- 4. Combine all tables ---
demo_mean_se_table <- rbind(
  sex_mean_se_table,
  age_mean_se_table,
  income_mean_se_table,
  religion_mean_se_table,
  urban_mean_se_table,
  children_mean_se_table,
  responsability_mean_se_table,
  country_mean_se_table,
  eatsafe_group_mean_se_table,
  infoseeking_mean_se_table,
  sandwich_mean_se_table,
  meat_mean_se_table,
  # --- ADDED NEW TABLES ---
  diary_mean_se_table,
  fresh_meat_mean_se_table
)

# Show the full table
print("Full weighted mean (SE) table (for Figure 3 data):")
print(demo_mean_se_table)

# --- 5. Create LaTeX table ---
latex_table_mean_se <- xtable(demo_mean_se_table, 
                              caption = 'Weighted Mean (Standard Error) of Q6_4 (Readability) by Characteristics, Product, and Survey Year', 
                              label = 'tab:demographics_mean_se')

# Print LaTeX code
print("LaTeX table code:")
print(latex_table_mean_se, type = "latex", booktabs = TRUE, include.rownames = FALSE)

```
## Data quality check: Food and You and National Diet and Nutrition Survey NDNS

I have analized and created the data set for NDNS. I have focused on reaty-to-eat meals. I calculated the prevalence of reporting these products from 2012 to 2018 by each individual from the data foodleveldietarydata. Then I integrate this calculation in the data set that contain individual details, including survey wrights, strata and psu. I recalculated the survey weight filtering the data only for adults 16+ and for years 2012-2018. I include the svy code to get a table/plot weighted for my publication.

```{r table22, echo=FALSE}

#National Diet and Nutrition Survey NDNS
#calculating sum of ready to meal for each individual
# Define the list of ready-to-meat product categories
ready_meal_categories <- c(
  "MANUFACTURED BEEF PRODUCTS INCLUDING READY MEALS",
  "MANUFACTURED CANNED TUNA PRODUCTS INCL READY MEALS", 
  "MANUFACTURED CHICKEN PRODUCTS INCL READY MEALS",
  "MANUFACTURED COATED CHICKEN / TURKEY PRODUCTS",
  "MANUFACTURED EGG PRODUCTS INCLUDING READY MEALS",
  "MANUFACTURED LAMB PRODUCTS INCLUDING READY MEALS",
  "MANUFACTURED MEAT PIES AND PASTRIES",
  "MANUFACTURED OILY FISH PRODUCTS INCL READY MEALS",
  "MANUFACTURED PORK PRODUCTS INCLUDING READY MEALS",
  "MANUFACTURED SHELLFISH PRODUCTS INCL READY MEALS",
  "MANUFACTURED WHITE FISH PRODUCTS INCL READY MEALS",
  "MEAT ALTERNATIVES INCL READY MEALS & HOMEMADE DISH",
  "OTHER MEAT PRODUCTS MANUFACTURED  INCL READY MEALS",
  "OTHER MEAT PRODUCTS MANUFACTURED INCL READY MEALS",
  "READY MEALS BASED ON SAUSAGES"
)

# Filter to only ready meal records
ready_meal_data5_6 <- ndns_data5_6[ndns_data5_6$SubFoodGroupDesc %in% ready_meal_categories, ]

# For each individual, sum the number of ready meal records
ready_meal_sum_ind5_6 <- aggregate(
  x = list(ready_meal_count5_6 = ready_meal_data5_6$SubFoodGroupDesc),
  by = list(seriali = ready_meal_data5_6$seriali),
  FUN = length
)


# Filter to only ready meal records
ready_meal_data7_8 <- ndns_data7_8[ndns_data7_8$SubFoodGroupDesc %in% ready_meal_categories, ]

# For each individual, sum the number of ready meal records
ready_meal_sum_ind7_8 <- aggregate(
  x = list(ready_meal_count7_8 = ready_meal_data7_8$SubFoodGroupDesc),
  by = list(seriali = ready_meal_data7_8$seriali),
  FUN = length
)

# Filter to only ready meal records
ready_meal_data9 <- ndns_data9[ndns_data9$SubFoodGroupDesc %in% ready_meal_categories, ]

# For each individual, sum the number of ready meal records
ready_meal_sum_ind9 <- aggregate(
  x = list(ready_meal_count9 = ready_meal_data9$SubFoodGroupDesc),
  by = list(seriali = ready_meal_data9$seriali),
  FUN = length
)

# Filter to only ready meal records
ready_meal_data10 <- ndns_data10[ndns_data10$SubFoodGroupDesc %in% ready_meal_categories, ]

# For each individual, sum the number of ready meal records
ready_meal_sum_ind10 <- aggregate(
  x = list(ready_meal_count10 = ready_meal_data10$SubFoodGroupDesc),
  by = list(seriali = ready_meal_data10$seriali),
  FUN = length
)

# Filter to only ready meal records
ready_meal_data11 <- ndns_data11[ndns_data11$SubFoodGroupDesc %in% ready_meal_categories, ]

# For each individual, sum the number of ready meal records
ready_meal_sum_ind11 <- aggregate(
  x = list(ready_meal_count11 = ready_meal_data11$SubFoodGroupDesc),
  by = list(seriali = ready_meal_data11$seriali),
  FUN = length
)

colnames(ready_meal_sum_ind9) <- c("seriali", "ready_meal_count")  
colnames(ready_meal_sum_ind10) <- c("seriali", "ready_meal_count")  
colnames(ready_meal_sum_ind11) <- c("seriali", "ready_meal_count")  

# Merge vertically (row bind)  
ready_meal_sum_ind9_11 <- rbind(ready_meal_sum_ind9, ready_meal_sum_ind10, ready_meal_sum_ind11)  
  
# Show the first few rows of the merged dataset  
print(head(ready_meal_sum_ind9_11)) 

#####################
#joining the data sets

# Use left join to keep all participants in ndns_5_6, even those without ready meals
ndns_dataind5_6 <- merge(ndns_dataind5_6, ready_meal_sum_ind5_6, by = "seriali", all.x = TRUE)
ndns_dataind7_8 <- merge(ndns_dataind7_8, ready_meal_sum_ind7_8, by = "seriali", all.x = TRUE)
ndns_dataind9_11 <- merge(ndns_dataind9_11, ready_meal_sum_ind9_11, by = "seriali", all.x = TRUE)
table(ndns_dataind5_6$ready_meal_count5_6, ndns_dataind5_6$surveyyr)
table(ndns_dataind7_8$ready_meal_count7_8, ndns_dataind7_8$surveyyr)

#subsets
#For example, if you are analysing the whole sample then astrata1 will be fine. But let’s say you’re analysing a subgroup e.g. aged 65+ then using astrata 1 will probably result in a number of single PSU strata. If there are a handful you can recode them appropriately (group them with adjacent strata within region) but if there are more than a few then you can try using astrata 2 instead. If there are still too many single PSU strata to recode then you would try astrata 3 and so on. I SELECT STRATA 5
#AREA is PSU
ndns_dataind5_6filter <- subset(ndns_dataind5_6, select = c("seriali", "SurveyYear", "age", "area", "astrata5", "wti_Y56", "ready_meal_count5_6"))
ndns_dataind7_8filter<- subset(ndns_dataind7_8, select = c("seriali", "surveyyr","age","area", "astrata5", "wti_Y78","ready_meal_count7_8"))
ndns_dataind9_11filter <- subset(ndns_dataind9_11, select = c("seriali", "surveyyr","AgeR","Area", "astrata5", "wti_Y911","ready_meal_count"))

colnames(ndns_dataind5_6filter) <- c("seriali", "SurveyYear", "age", "area", "astrata5", "wti","ready_meal_count")  
colnames(ndns_dataind7_8filter) <- c("seriali", "SurveyYear", "age", "area", "astrata5", "wti","ready_meal_count")  
colnames(ndns_dataind9_11filter) <- c("seriali", "SurveyYear", "age", "area", "astrata5", "wti","ready_meal_count")  

# Merge vertically (row bind)  
ndns_dataindtotal <- rbind(ndns_dataind5_6filter, ndns_dataind7_8filter, ndns_dataind9_11filter) 
# Export the data frame to an Excel file
write_xlsx(ndns_dataindtotal, path = "ndns_dataindtotal.xlsx")

# Step 1: Filter for participants aged 16 
ndns_dataindtotal_16 <- ndns_dataindtotal[ndns_dataindtotal$age >= 16,]
# Calculate the sum of weights for each survey group
sum_wti_56 <- sum(ndns_dataindtotal_16$wti[ndns_dataindtotal_16$SurveyYear %in% c(5,6)], na.rm=TRUE)
sum_wti_78 <- sum(ndns_dataindtotal_16$wti[ndns_dataindtotal_16$SurveyYear %in% c(7,8)], na.rm=TRUE)
sum_wti_911 <- sum(ndns_dataindtotal_16$wti[ndns_dataindtotal_16$SurveyYear %in% c(9,10,11)], na.rm=TRUE)
total_sum_wti <- sum(ndns_dataindtotal_16$wti, na.rm=TRUE)


# Step 3: Calculate the rescaled weights for each group
# Initialize the new weight variable
ndns_dataindtotal_16$wti_rescaled <- 0
# For Years 5 & 6: multiply by 2/11
ndns_dataindtotal_16$wti_rescaled[ndns_dataindtotal_16$SurveyYear %in% c(5,6)] <- 
  ndns_dataindtotal_16$wti[ndns_dataindtotal_16$SurveyYear %in% c(5,6)] * total_sum_wti / sum_wti_56 * (2/11)

# For Years 7 & 8: multiply by 2/11
ndns_dataindtotal_16$wti_rescaled[ndns_dataindtotal_16$SurveyYear %in% c(7,8)] <- 
  ndns_dataindtotal_16$wti[ndns_dataindtotal_16$SurveyYear %in% c(7,8)] * total_sum_wti / sum_wti_78 * (2/11)

# For Years 9, 10 & 11: multiply by 3/11
ndns_dataindtotal_16$wti_rescaled[ndns_dataindtotal_16$SurveyYear %in% c(9,10,11)] <- 
  ndns_dataindtotal_16$wti[ndns_dataindtotal_16$SurveyYear %in% c(9,10,11)] * total_sum_wti / sum_wti_911 * (3/11)

# Step 4: Re-scale the weights to have a mean of 1
mean_rescaled_weight <- mean(ndns_dataindtotal_16$wti_rescaled, na.rm=TRUE)
ndns_dataindtotal_16$wti_final <- ndns_dataindtotal_16$wti_rescaled / mean_rescaled_weight
write_xlsx(ndns_dataindtotal_16, path = "ndns_dataindtotal_16.xlsx") #average =1

########## Survey desing

options(survey.lonely.psu = "adjust") #specify how variance estimation will be handled in cases where a stratum contains only one PSU
options(survey.adjust.domain.lonely = TRUE) # specify how variance estimation will be handled in cases where a stratum contains only one PSU. These options “center the stratum at the population mean rather than the stratum mean” and make the same adjustment within subgroup analyses

survey_design2 <- svydesign(  
    id = ~area,  
    strata = ~astrata5,  
    weights = ~wti_final,  
    data = ndns_dataindtotal_16,  
    nest = TRUE  
) 

#information of clusters and stratas
survey_design2

# Weighted barplot
mybar2 <- svytable(~factor(ready_meal_count), survey_design2, Ntotal=1)
barplot(mybar2,
        ylab = "Proportion", xlab = "Ready meal",
        main = "Weighted", cex.names = 0.65)


# Calculate the weighted prevalence (number and proportion) of ready-to-eat meals by year
# We'll treat ready_meal_count > 0 as having consumed a ready meal
ndns_dataindtotal_16$ready_meal_any <- ifelse(is.na(ndns_dataindtotal_16$ready_meal_count), 0, ifelse(ndns_dataindtotal_16$ready_meal_count > 0, 1, 0))

# Update the survey design to include this new variable
design2 <- update(survey_design2, ready_meal_any = ndns_dataindtotal_16$ready_meal_any)

# Calculate weighted prevalence (number and proportion) by year
# Proportion
prop_by_year <- svyby(~ready_meal_any, ~SurveyYear, design2, svymean, na.rm=TRUE)
# Number (weighted count)
count_by_year <- svyby(~ready_meal_any, ~SurveyYear, design2, svytotal, na.rm=TRUE)

print("Weighted proportion of adults consuming ready meals by year:")
print(prop_by_year)

print("Weighted number of adults consuming ready meals by year:")
print(count_by_year)

# Calculate total weighted count of all individuals by year (not just ready meal consumers)
total_count_by_year <- svyby(~I(rep(1, length(ready_meal_any))), ~SurveyYear, design2, svytotal, na.rm=TRUE)


print("Weighted total number of adults (all individuals) by year:")
print(total_count_by_year)


#### Merging data sets

# Create the comprehensive table as requested
# First, create the NDNS data with all years and SE values
ndns_complete <- data.frame(
  SurveyYear = c(5, 6, 7, 8, 9, 10, 11),
  Years = c(2012, 2013, 2014, 2015, 2016, 2017, 2018),
  Prevalence_NDNS = c(0.6671244, 0.6299603, 0.6125167, 0.6271443, 0.666476, 0.6633179, 0.7005119),
  SE_NDNS = c(0.02180248, 0.02270312, 0.02312585, 0.02123973, 0.02265036, 0.02273316, 0.02199741)
)

# Create Food & You data for the specific years (2012, 2014, 2016, 2018)
food_you_data <- data.frame(
  Years = c(2012, 2014, 2016, 2018),
  Weekly_Sandwich = c(50.1, 50.0, 46.6, 37.9),
  Monthly_Sandwich = c(32.4, 31.2, 36.0, 42.0),
  Never_Sandwich = c(17.4, 18.9, 17.4, 20.1),
  Weekly_Precooked = c(16.2, 17.1, 19.8, 20.8),
  Monthly_Precooked = c(17.9, 19.0, 25.4, 28.8),
  Never_Precooked = c(65.9, 63.8, 54.9, 50.5)
)

# Merge the datasets
comprehensive_table <- merge(ndns_complete, food_you_data, by = "Years", all.x = TRUE)

# Reorder columns to match the requested format
comprehensive_table <- comprehensive_table[, c("SurveyYear", "Years", "Prevalence_NDNS", "SE_NDNS", 
                                               "Weekly_Sandwich", "Monthly_Sandwich", "Never_Sandwich",
                                               "Weekly_Precooked", "Monthly_Precooked", "Never_Precooked")]

# Rename columns to match the exact format requested
colnames(comprehensive_table) <- c("SurveyYear", "Years", "Prevalence NDNS", "SE NDNS", 
                                   "Weekly Sand", "Monthly Sand", "Never sand",
                                   "Weekly Cmeat", "Monthly Cmeat", "Never Cmeat")

print('Comprehensive table:')
print(comprehensive_table)

# Save to file
write.csv(comprehensive_table, "comprehensive_consumption_table.csv", row.names = FALSE)
print('Table saved to comprehensive_consumption_table.csv')

# Convert to long format for plotting
library(tidyr)
plot_data_long <- comprehensive_table %>%
  pivot_longer(cols = c("Prevalence NDNS", "Weekly Sand", "Monthly Sand", "Never sand"), 
               names_to = "Category", values_to = "Percentage")

# Create the plot
p <- ggplot(plot_data_long, aes(x = Years, y = Percentage, color = Category)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  labs(title = 'NDNS Ready Meal Prevalence vs Sandwich Consumption (2012-2018)',
       y = 'Percentage (%)', 
       x = 'Year',
       color = 'Category') +
  theme_minimal() +
  scale_x_continuous(breaks = c(2012, 2014, 2016, 2018)) +
  scale_color_manual(values = c(
    'NDNS_Prevalence' = '#e41a1c',
    'Weekly_Sand' = '#377eb8',
    'Monthly_Sand' = '#4daf4a',
    'Never_Sand' = '#984ea3'
  ),
  labels = c(
    'NDNS_Prevalence' = 'NDNS Ready Meal Prevalence',
    'Weekly_Sand' = 'Sandwich - Weekly',
    'Monthly_Sand' = 'Sandwich - Monthly',
    'Never_Sand' = 'Sandwich - Never'
  )) +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9)) +
  ylim(0, 80)

print(p)



```

## Readability mean table weighted PLOT


```{r table22, echo=FALSE}

# Load required libraries
library(tidyverse)
library(patchwork)

# Create the dataframe using tribble, now updated with the new table values
readability_data <- tribble(
  ~Variable, ~Category, ~Year, ~Mean, ~SD,
  # Age - Using three representative groups from your table
  "Age", "16-24", 2012, 3.91, 0.12,
  "Age", "16-24", 2014, 4.03, 0.11,
  "Age", "16-24", 2016, 3.90, 0.14,
  "Age", "16-24", 2018, 4.23, 0.12,
  "Age", "45-54", 2012, 2.88, 0.07,
  "Age", "45-54", 2014, 2.91, 0.07,
  "Age", "45-54", 2016, 2.85, 0.06,
  "Age", "45-54", 2018, 2.58, 0.05,
  "Age", "65+",   2012, 3.11, 0.08,
  "Age", "65+",   2014, 3.21, 0.07,
  "Age", "65+",   2016, 3.16, 0.08,
  "Age", "65+",   2018, 3.18, 0.09,
  # Income (from hhdinc_group)
  "Income", "Low income", 2012, 3.30, 0.06,
  "Income", "Low income", 2014, 3.31, 0.05,
  "Income", "Low income", 2016, 3.20, 0.07,
  "Income", "Low income", 2018, 3.13, 0.06,
  "Income", "High income", 2012, 3.59, 0.05,
  "Income", "High income", 2014, 3.55, 0.05,
  "Income", "High income", 2016, 3.51, 0.05,
  "Income", "High income", 2018, 3.53, 0.05,
  # Religion (from Religion_DV)
  "Religion", "Christian", 2012, 3.67, 0.07,
  "Religion", "Christian", 2014, 3.68, 0.05,
  "Religion", "Christian", 2016, 3.51, 0.06,
  "Religion", "Christian", 2018, 3.71, 0.06,
  "Religion", "Other religion", 2012, 3.35, 0.05,
  "Religion", "Other religion", 2014, 3.33, 0.05,
  "Religion", "Other religion", 2016, 3.31, 0.05,
  "Religion", "Other religion", 2018, 3.11, 0.05,
  "Religion", "No religion", 2012, 3.60, 0.16,
  "Religion", "No religion", 2014, 3.33, 0.21,
  "Religion", "No religion", 2016, 3.54, 0.16,
  "Religion", "No religion", 2018, 3.67, 0.15,
  # Area (from UrbanRuralInd)
  "Area", "Urban", 2012, 3.50, 0.04,
  "Area", "Urban", 2014, 3.47, 0.04,
  "Area", "Urban", 2016, 3.41, 0.05,
  "Area", "Urban", 2018, 3.46, 0.05,
  "Area", "Rural", 2012, 3.21, 0.12,
  "Area", "Rural", 2014, 3.32, 0.10,
  "Area", "Rural", 2016, 3.32, 0.08,
  "Area", "Rural", 2018, 3.17, 0.09,
  # Children under 16 (from below16)
  "Children under 16", "Yes", 2012, 3.35, 0.05,
  "Children under 16", "Yes", 2014, 3.31, 0.05,
  "Children under 16", "Yes", 2016, 3.24, 0.05,
  "Children under 16", "Yes", 2018, 3.23, 0.05,
  "Children under 16", "No", 2012, 3.75, 0.07,
  "Children under 16", "No", 2014, 3.78, 0.06,
  "Children under 16", "No", 2016, 3.75, 0.06,
  "Children under 16", "No", 2018, 3.75, 0.07,
  # Shopping responsibilities (from Q3_1)
  "Shopping responsibilities", "All/Most", 2012, 3.38, 0.05,
  "Shopping responsibilities", "All/Most", 2014, 3.40, 0.04,
  "Shopping responsibilities", "All/Most", 2016, 3.37, 0.05,
  "Shopping responsibilities", "All/Most", 2018, 3.31, 0.05,
  "Shopping responsibilities", "Sometimes/Never", 2012, 3.55, 0.06,
  "Shopping responsibilities", "Sometimes/Never", 2014, 3.51, 0.05,
  "Shopping responsibilities", "Sometimes/Never", 2016, 3.42, 0.06,
  "Shopping responsibilities", "Sometimes/Never", 2018, 3.48, 0.06,
  # Concerns about safe eating (from eatsafe_group)
  "Concerns about safe eating", "High", 2012, 3.46, 0.05,
  "Concerns about safe eating", "High", 2014, 3.46, 0.04,
  "Concerns about safe eating", "High", 2016, 3.45, 0.04,
  "Concerns about safe eating", "High", 2018, 3.38, 0.05,
  "Concerns about safe eating", "Low", 2012, 3.46, 0.08,
  "Concerns about safe eating", "Low", 2014, 3.45, 0.09,
  "Concerns about safe eating", "Low", 2016, 3.18, 0.10,
  "Concerns about safe eating", "Low", 2018, 3.43, 0.08,
  # Information seeking (from Q11_8b25)
  "Information seeking", "Yes", 2012, 3.33, 0.09, # Assuming 1 is Yes
  "Information seeking", "Yes", 2014, 3.19, 0.09,
  "Information seeking", "Yes", 2016, 3.09, 0.09,
  "Information seeking", "Yes", 2018, 3.21, 0.09,
  "Information seeking", "No", 2012, 3.50, 0.05, # Assuming 0 is No
  "Information seeking", "No", 2014, 3.50, 0.04,
  "Information seeking", "No", 2016, 3.46, 0.04,
  "Information seeking", "No", 2018, 3.44, 0.05,
  # Sandwich Consumption
  "Pre-package Sandwich", "Never", 2012, 3.78, 0.09,
  "Pre-package Sandwich", "Never", 2014, 3.75, 0.09,
  "Pre-package Sandwich", "Never", 2016, 3.64, 0.09,
  "Pre-package Sandwich", "Never", 2018, 3.66, 0.09,
  "Pre-package Sandwich", "Monthly", 2012, 3.59, 0.06,
  "Pre-package Sandwich", "Monthly", 2014, 3.46, 0.06,
  "Pre-package Sandwich", "Monthly", 2016, 3.45, 0.06,
  "Pre-package Sandwich", "Monthly", 2018, 3.36, 0.06,
  "Pre-package Sandwich", "Weekly", 2012, 3.27, 0.06,
  "Pre-package Sandwich", "Weekly", 2014, 3.34, 0.05,
  "Pre-package Sandwich", "Weekly", 2016, 3.25, 0.05,
  "Pre-package Sandwich", "Weekly", 2018, 3.28, 0.07,
  # Pre-cooked Meat Consumption
  "Pre-cooked Meat", "Never", 2012, 3.45, 0.05,
  "Pre-cooked Meat", "Never", 2014, 3.46, 0.05,
  "Pre-cooked Meat", "Never", 2016, 3.44, 0.05,
  "Pre-cooked Meat", "Never", 2018, 3.38, 0.05,
  "Pre-cooked Meat", "Monthly", 2012, 3.63, 0.09,
  "Pre-cooked Meat", "Monthly", 2014, 3.48, 0.08,
  "Pre-cooked Meat", "Monthly", 2016, 3.36, 0.09,
  "Pre-cooked Meat", "Monthly", 2018, 3.45, 0.09,
  "Pre-cooked Meat", "Weekly", 2012, 3.36, 0.08,
  "Pre-cooked Meat", "Weekly", 2014, 3.42, 0.08,
  "Pre-cooked Meat", "Weekly", 2016, 3.33, 0.07,
  "Pre-cooked Meat", "Weekly", 2018, 3.37, 0.07,
  
  # --- NEW DATA ADDED BELOW ---
  
  # Diary Consumption (from consumption_diary)
  "Diary", "Never", 2012, 3.47, 0.04,
  "Diary", "Never", 2014, 3.46, 0.04,
  "Diary", "Never", 2016, 3.40, 0.04,
  "Diary", "Never", 2018, 3.39, 0.04,
  "Diary", "Monthly", 2012, 3.44, 0.29,
  "Diary", "Monthly", 2014, 3.55, 0.27,
  "Diary", "Monthly", 2016, 3.22, 0.30,
  "Diary", "Monthly", 2018, 3.53, 0.19,
  "Diary", "Weekly", 2012, 3.30, 0.29,
  "Diary", "Weekly", 2014, 3.00, 0.23,
  "Diary", "Weekly", 2016, 3.20, 0.25,
  "Diary", "Weekly", 2018, 3.36, 0.19,
  # Fresh Meat Consumption (from consumption_meat)
  "Fresh Meat", "Never", 2012, 3.47, 0.09,
  "Fresh Meat", "Never", 2014, 3.47, 0.07,
  "Fresh Meat", "Never", 2016, 3.44, 0.07,
  "Fresh Meat", "Never", 2018, 3.37, 0.06,
  "Fresh Meat", "Monthly", 2012, 3.44, 0.05,
  "Fresh Meat", "Monthly", 2014, 3.47, 0.05,
  "Fresh Meat", "Monthly", 2016, 3.38, 0.05,
  "Fresh Meat", "Monthly", 2018, 3.35, 0.05,
  "Fresh Meat", "Weekly", 2012, 3.73, 0.14,
  "Fresh Meat", "Weekly", 2014, 3.30, 0.13,
  "Fresh Meat", "Weekly", 2016, 3.37, 0.10,
  "Fresh Meat", "Weekly", 2018, 3.65, 0.11
)

# --- UPDATED AND MORE ROBUST PLOTTING LOGIC ---

# Define the desired 5x3 plot order
final_plot_order <- c("Age", "Income", "Religion", 
                      "Children under 16", "Area", "Country", 
                      "Shopping responsibilities", "Concerns about safe eating", "Information seeking",
                      "Pre-package Sandwich", "Pre-cooked Meat", "Diary", 
                      "Fresh Meat") # Added new products, 13 total

# Generate plots in the correct order from the start
plot_list_ordered <- readability_data %>%
  # Convert Variable to a factor with the desired order to ensure correct sequencing
  mutate(Variable = factor(Variable, levels = final_plot_order)) %>%
  # Group by this new factor
  group_by(Variable) %>%
  # Create a list of data frames, which will be in the correct order
  group_split() %>%
  # Use map to iterate over the ordered list of data frames and create a plot for each
  purrr::map(~ ggplot(.x, aes(Year, Mean, colour = Category, group = Category)) +
        geom_line(linewidth = 1) +
        geom_point(size = 2) +
        geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = 0.2) +
        scale_x_continuous(breaks = c(2012, 2014, 2016, 2018)) +
        scale_y_continuous(limits = c(2.5, 4.5)) +
        scale_colour_grey(start = 0.2, end = 0.7) +
        theme_minimal(base_size = 14) +
        theme(legend.position = "bottom", legend.title = element_blank()) +
        # Use the first value of the Variable column as the title for each plot
        labs(title = first(.x$Variable), x = "Year", y = "Mean (± SD)")
  )

# Combine the 13 ordered plots into one 5x3 multi-panel figure
combined_plot <- wrap_plots(plot_list_ordered, ncol = 3, nrow = 5) + # MODIFIED: nrow = 5
  plot_annotation(
    title = "",
    # Add a theme to control the main title's appearance
    theme = theme(plot.title = element_text(size = 22, face = "bold"))
  )

# Print the final combined plot
print(combined_plot)

# Save the final plot to a file ----------------------------------------------------
# MODIFIED: Increased height to accommodate the extra row of plots
ggsave("readability_5x3_grid.png",
       plot = combined_plot,
       width = 12, height = 16, dpi = 300, bg = "white") # MODIFIED: height = 16

cat("Exported readability_5x3_grid.png\n")


```

## Ordinal logistic regression FSA df_full 2012-2018 -  no proportional odds weighted Sandwich and precooked meat + readability proportional odd - REVERSE CAUSALITY

```{r reverse, echo=FALSE}

gen22r <- svy_vglm(
  Q6_4  ~ consumption_sandwich*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = ~  consumption_sandwich + factor(Religion_DV) + hhdinc_group + below16 + marstat2 + factor(Country_DV) + consumption_sandwich*factor(surveyyear)),
  design = survey_design.nomiss)

summary(gen22r)

gen44 <- svy_vglm(
  Q6_4 ~ consumption_precookedmeat*factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = cumulative(parallel = ~ consumption_precookedmeat + RespSex + age + factor(Religion_DV) + UrbanRuralInd + below16 + marstat2 + Q3_1 + factor(Country_DV) + consumption_precookedmeat*factor(surveyyear)),
  design = survey_design.nomiss
)

summary(gen44)


```

## Logistic regression FSA df_full 2012-2018 -  no proportional odds weighted Sandwich and precooked meat

```{r reverse, echo=FALSE}

# Logistic regression for sandwich consumption
gen22r_logistic <- svyglm(
  consumption_sandwich_binary ~ Q6_4 * factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = binomial(link = "logit"),
  design = survey_design.nomiss)

summary(gen22r_logistic)

# Logistic regression for pre-cooked meat consumption
gen44_logistic <- svyglm(
  consumption_precookedmeat_binary ~ Q6_4 * factor(surveyyear) + RespSex + age + factor(Religion_DV) + hhdinc_group + UrbanRuralInd + below16 + bhhsize + marstat2 + Q3_1 + factor(Country_DV),
  family = binomial(link = "logit"),
  design = survey_design.nomiss)

summary(gen44_logistic)


```



